---
title: "The slumdown package"
author: "Danielle Navarro"
date: "10 May 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/djnavarro/slumdown.svg?branch=master)](https://travis-ci.org/djnavarro/slumdown) [![Codecov test coverage](https://codecov.io/gh/djnavarro/slumdown/branch/master/graph/badge.svg)](https://codecov.io/gh/djnavarro/slumdown?branch=master) ![Lifecycle experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg) [![CRAN status](https://www.r-pkg.org/badges/version/slumdown)](https://cran.r-project.org/package=slumdown)
<!-- badges: end -->

The *slumdown* package is an experiment in creating a simple "blogdown native" Hugo theme, one that assumes that posts are written using R Markdown. It extends the [slum theme for Hugo](https://github.com/djnavarro/hugo-slum) by providing an interface for customising the blog within R and a system for generating plots that use the same colour scheme as the blog post. The *slumdown* package is only available on GitHub:

```{r install, eval=FALSE}
remotes::install_github("djnavarro/slumdown")
```

By default, the *slumdown* package assumes the source code for the site takes the form of an RStudio project, and will be deployed to GitHub pages, though neither is strictly necessary. To get started:

```{r eval=FALSE}
slumdown::new_slum("desired/path/to/my/blog") 
```

This will create a new RStudio project called `blog` (or whatever), download the slum theme and the example site. From within the project, initialise the blog using `blogdown`:

```{r eval=FALSE}
blogdown::serve_site()
```

Blogdown will then generate the [example site](https://djnavarro.github.io/hugo-slum/) in the `docs` folder, which provides a short tutorial on how to get started using the package and what it is capable of. 

## Warning!

On the off chance that anyone plans to use this other than me... probably not a good idea right now. It is *very* experimental, I'm using it largely as a method of teaching myself new things, and no part of the API is stable at the moment.
