---
title: "The slumdown package"
author: "Danielle Navarro"
date: "14 April 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[![Travis build status](https://travis-ci.org/djnavarro/slumdown.svg?branch=master)](https://travis-ci.org/djnavarro/slumdown)


```{r install}
# devtools::install_github("djnavarro/slumdown")
library("slumdown")
```

Create a new blogdown site using the [slum theme](https://github.com/djnavarro/hugo-slum). By default, the blog is 
created in a new RStudio project, and is configured to publish to the "docs"
folder (to make it easier to publish to github pages)


```{r eval=FALSE}
# create a new slumdown blog & rstudio project 
# NOT RUN:
slum_new() 
```

List the palettes (will throw an error if it cannot find the theme)

```{r eval=FALSE}
slum_palettes()
```

Function to create a new palette...

The `theme_slum()` function provides ggplot2 themes that are consistent with the different slum colour schemes.

```{r, warning=FALSE}
library(ggplot2)
p <- ggplot(mpg, aes(displ, hwy)) + geom_point()
p + theme_slum("light")
p + theme_slum("dark")
p + theme_slum("kunoichi")
```

