---
title: "The slumdown package"
author: "Danielle Navarro"
date: "21 April 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[![Travis build status](https://travis-ci.org/djnavarro/slumdown.svg?branch=master)](https://travis-ci.org/djnavarro/slumdown)

The *slumdown* package is an experiment in creating a simple "blogdown native" Hugo theme, one that assumes that posts are written using R Markdown. It extends the [slum theme for Hugo](https://github.com/djnavarro/hugo-slum) by providing an interface for customising the blog within R and a system for generating plots that use the same colour scheme as the blog post. The *slumdown* package is not on CRAN and so needs to be installed from GitHub:

```{r install}
# devtools::install_github("djnavarro/slumdown")
library("slumdown")
```

By default, the *slumdown* package assumes the source code for the site takes the form of an RStudio project, and will be deployed to GitHub pages, though neither is strictly necessary. To get started:

```{r eval=FALSE}
slum_new(dir = "path/to/my/slumblog") 
```

This will create a new RStudio project called `slumblog` (or whatever), download the slum theme and the example site. From within the project, initialise the blog using `blogdown`:

```{r eval=FALSE}
blogdown::serve_site()
```

Blogdown will then generate the [example site](https://djnavarro.github.io/hugo-slum/) in the `docs` folder, which provides a short tutorial on how to get started using the package and what it is capale of. 
