---
title: "SLUM"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The *slum* theme for Hugo is an adaptation Yihue Xie's *Xmin* theme that borrows stylistic elements from the Tufte R Markdown theme and from the *academic* Hugo theme. I'm not really convinced it's useful for much, hence the name; this is a *somewhat-light unhelpfully-minimal* Hugo theme. In truth, my main goal in putting this theme together was to make sure I understand the basics of how Hugo works. 

## Getting started

To create the example site using the slum template into a fresh directory:

```{r, eval=FALSE}
blogdown::new_site(
  dir = "~/../Desktop/slum", 
  theme = "djnavarro/hugo-slum",
  theme_example = TRUE,
  sample = FALSE
)
```

By setting `theme_example = TRUE` (the default) it installs the example site, 
and by setting `sample = FALSE` it prevents Hugo from automatically including
the default content.

To serve an existing site, assuming that R the working directory is set to
the home directory for the site:

```{r, eval=FALSE}
blogdown::serve_site()
```

The example site serves as a tutorial in how to use the theme, and you can see it at:

https://djnavarro.github.io/hugo-slum/




